---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

read in data frame: minwage.csv
```{r}

```

explore your data 
```{r}
str(minwage)
head(minwage)
rownames
colnames
summary(minwage)
```

visualize your data (start with fullAfter)
```{r}
plot(minwage$fullAfter,type = "l")
points(minwage$fullAfter)#add points by points() argument
boxplot(minwage$fullAfter)
```

check if your assumptions about visualization is correct
```{r}
summary(minwage$fullAfter)
```

let's look at characteristics
```{r}
mean(minwage$fullAfter)
median
```

create a baby dataset
```{r}
women <- runif(50, min= 37, max = 83)
men <- runif(50, min = 10, max=40)
kiwi <- cbind(women,men)
kiwi <- as.data.frame(kiwi)
#or
kiwi_2 <- data.frame(women,men)
identical(kiwi,kiwi_2)
```

explore your new baby data
```{r}
kiwi
summary(kiwi)
str(kiwi)
head(kiwi)
```

visualize your new baby data
```{r}
plot(kiwi$men,type="l")
points(kiwi$men)
boxplot(kiwi$men)
plot(kiwi$women)
boxplot(kiwi$women)
```

create another babyset with column names
```{r}
women <- c(18,66,29,42)
men <- c(34,97,108,12)
kiwi <- rbind(women,men)
kiwi <- as.data.frame(kiwi)
colnames(kiwi) <- c("Monday","Tuesday","Wednesday","Saturday")
kiwi
```

explore your new baby data
```{r}
str(kiwi)
summary(kiwi)
mean(kiwi$Tuesday)
```

visualize your new baby data (visualizing new kiwi data is not necessary)
```{r}
plot(kiwi$Monday)
```

create a vector with specific mean and sd (set seed for 200)
```{r}
set.seed(500)
a <- rnorm(500,mean = 7, sd = 3)
mean(a)
a
sd(a)
median(a)
class(a)
summary(a)
```

visualize your vector
```{r}
boxplot(a) #normal distribution?
plot(a,type = "l")
points(a)
```

create a plot by using one of the variables from winwage. Assign axis names and color
```{r}
plot(minwage$fullBefore, type = "l", col = "blue", xlab = "time", ylab = "wage_after", main = "hello")
```

create a data frame by using runif() and visualize it with plot()
```{r}
tea <- runif(35, min = 70, max = 138)
time <- 1:35
tea_time <- data.frame(time,tea)
plot(tea_time, type = "l", col = "blue", xlab = "time", ylab = "tea", main = "TEA TIME")
points(tea_time)
tea_time
```

create another dataset by using rnorm() and set seed for 150. Then visualize it with plot()
```{r}
set.seed(150)
germs <- rnorm(47, mean = 3, sd = 7)
time <- 10:56
germs_time <- data.frame(time,germs)
plot(germs_time, type = "l", col = "red", xlab = "time", ylab = "germs", main = "Germs Time")
points(germs_time)
boxplot(germs_time)
```


















