---
title: "POLS_203_DS_5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

read in data frame: minwage.csv
```{r}

```

explore your data with str(), head(), rownames(), colnames(), summary()
```{r}

```

visualize your data (start with fullAfter or any variable you want. You can also use pairs())
```{r}

```

check if your assumptions about visualization is correct
```{r}

```

look at the characteristics of your data
```{r}

```

create a baby data frame with runif()
```{r}

```

explore your new baby data
```{r}

```

visualize your new baby data with plot(), boxplot()
```{r}

```

create another baby data frame and assign column names
Hint: Assigning less amount of measurements to your vectors might make life easier for you
```{r}

```

explore your new baby data
```{r}

```

visualize your new baby data (optional)
```{r}

```

create a vector with specific mean and sd (set seed for 200)
```{r}

```

visualize your vector
```{r}

```

create a plot by using one of the variables from winwage. Assign axis names and color
```{r}

```

create a data frame by using runif() and visualize it with plot()
```{r}

```

create another dataset by using rnorm() and set seed for 150. Then visualize it wiht plot()
```{r}

```










