---
title: "POLS 203 DS 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

FUNCTIONS
#previous examples
class(), sqrt(), print(), c()
```{r}
number_apple<-c(10,20,40,65,79)
length(number_apple)

min(number_apple)
max(number_apple)
range(number_apple) #smallest and biggest numbers
mean(number_apple)
sum(number_apple)

```

seq(), a vector composed of increasing or decreasing values
```{r}
year<-seq(from=1860,to=1960,by=10)
year
year<-seq(from=1980,to=1900,by=-10)
year
```

names()
```{r}
names(year)<-c('Peach','Banana','Apple','Pineapple','Orange','Cherry','Grape','Plum','Pear')
year
#or
fruits_produced<-c('Peach','Banana','Apple','Pineapple','Orange','Cherry','Grape','Plum','Pear')
names(year)<-fruits_produced
year
```

CREATING YOUR OWN FUNCTION
```{r}
my_function<-function(x){   #first input
  s.out<-sum(x)
  l.out<-length(x)
  m.out<-s.out/l.out
  out<-c(s.out,l.out,m.out)  #this is the output
  names(out)<-c('Sum','Length','Mean')
  return(out)  #ending our function by calling the output
}

a<-1:100 #1'den 100'e kadar değerler
my_function(a)
my_function(number_apple)
```

DATA FILES

generally csv files. Session > Set Working Directory > Choose Directory. Put a single file into a folder then choose the file and work with it

computer data set will be used for the following exercises
```{r}
comp<-read.csv('computer.csv',stringsAsFactors = FALSE,header = TRUE)
class(comp)
```

DATA FRAMES
```{r}
comp<-read.csv('computer.csv',stringsAsFactors = FALSE ,header = TRUE)
names(comp)
nrow(comp)
ncol(comp)
dim(comp)
```

```{r}
#there are also data frames in R. You can access them by typing data()
data("OrchardSprays")
class(data)
os <- as.data.frame(OrchardSprays)
summary(os)
```

```{r}
str(comp)
summary(comp)
dim(comp) #... amount of observations, .... amount of variables
head(comp)
tail(comp)
```

```{r}
comp$price # $ for accessing specific columns 
comp$hd
comp$screen
```

YOU CAN ALSO USE INDEXING TO RETRIEVE INDIVIDUAL VARIABLES []
```{r}
comp[,'price']
comp[,'price']
comp[c(1,2),] #first two rows and all columns
comp[c(1,2),]
comp[1:3,'price'] #first three values of the price column
comp[,1:4] #first 4 columns and all the rows
comp[1:10,] #first 10 observations of comp
comp[1:10,4] #first ten observations of the hd column
```

```{r}
comp$price[seq(from=1,to=nrow(comp),by=20)] #take elements 1,21... of the 'price' variable
```

NAs
```{r}
is.na(comp)
comp<-na.omit(comp)
comp
```
