---
title: "POLS 203 PS 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

USING R AS A CALCULATOR

```{r}
5 + 8 
12 - 4
5 / 3
6 * 8
7 ^ 6
sqrt(16) #sqrt() is a function
```

OBJECTS
```{r}
result<-4 + 9
print(result) #console'a yazarken print fonksiyonunu kullanmaya gerek yok
result
```

BE CAREFUL!!! OBJECT NAMES ARE SENSITIVE. result and RESULT will not give the same returns

Different types of values as objects
```{r}
fruit<-'apple'
number<-'3' #here, 3 is not numeric but categorical
#SOME EXAMPLES
money<-2500
sqrt(money)
money/50
money*4
```

class()
```{r}
class(money)
class(fruit)
class(number)
c_money <- as.character(money)
c_fruit <- as.numeric(fruit) #see the mistake in here!!!
```

VECTORS
```{r}
number_apple<-c(3,4,7,5,1)
number_banana<-c(2,3,1,9,16)
number_fruit<-c(number_banana,number_apple)
number_fruit
length(number_fruit)

#you can do calculations with these vectors since they are numeric
number_apple_2<-number_apple*2
number_banana_3<-number_banana*3
fruit_rate<-number_apple/number_banana #if we want express numbers of apple as a proportion of bananas
number_apple[c(1,2)]<-c(1,8) #replacing the values
number_apple  
```

INDEXING (to access specific elements)
```{r}
number_apple[1]
number_banana[c(3,5)]
number_apple[-1]
```

FUNCTIONS
#previous examples
class(), sqrt(), print(), c()
```{r}
length(number_apple)
min(number_apple)
max(number_apple)
range(number_apple) #smallest and biggest numbers
mean(number_apple)
sum(number_apple)
mode(number_apple)
```

seq(), a vector composed of increasing or decreasing values
```{r}
year<-seq(from=1860,to=1960,by=10)
year<-seq(from=1980,to=1900,by=-10)
year
```

names()
```{r}
names(year)<-c('Peach','Banana','Apple','Pineapple','Orange','Cherry','Grape','Plum','Pear')
year
#or
fruits_produced<-c('Peach','Banana','Apple','Pineapple','Orange','Cherry','Grape','Plum','Pear')
names(year)<-fruits_produced
year
```

CREATING YOUR OWN FUNCTION
```{r}
my_function<-function(x){   #first input
  s.out<-sum(x)
  l.out<-length(x)
  m.out<-s.out/l.out
  out<-c(s.out,l.out,m.out)  #this is the output
  names(out)<-c('Sum','Length','Mean')
  return(out)  #ending our function by calling the output
}

a<-1:100 #1'den 100'e kadar değerler
my_function(a)
my_function(number_apple)
```

DATA FILES

generally csv files. Session > Set Working Directory > Choose Directory. Put a single file into a folder then choose the file and work with it

computer data set will be used for the following exercises
```{r}
comp<-read.csv('computer.csv',stringsAsFactors = FALSE,header = TRUE)
class(comp)
```





